Simulation of an Attic Fire in a Wood Frame Residential Structure - Chicago, IL

### 2015-09-01 Studies/2012_Chicago/Report/firetech_chicago.tex
Add files for FireTech pub

In Fig.~\ref{fig:hrr}, the solid line represents the baseline FDS simulation (this follows the noted door openings from the incident). The dashed line represents an alternative series of events in which the rear door does not get opened and the subsequent breach of the rear porch wall on the left side of the structure does not occur. The dash-dotted line represents the prescribed (or nominal) HRR that was input into FDS. As shown in Fig.~\ref{fig:hrr}, the HRR output from FDS is less than the prescribed HRR because the fire in the structure becomes ventilation limited. The maximum HRR value is slightly less than 9~MW before the fire becomes ventilation limited and begins to decay. The HRR is reduced to 5~MW as the oxygen inside the structure is consumed. There is an insufficient amount of oxygen in the structure to burn all of the fuel, therefore combustion occurs locally at the vents where fresh air is available. Figure~\ref{fig:smv_ext_fire} shows flaming combustion through the failed window on the rear side of the structure and attic breach just after the second fire ignites at 40~s. Figure~\ref{fig:smv_ext_fire} also shows a photograph taken during an attic fire experiment that confirms this type of fire behavior. As a fire becomes underventilated, the majority of the combustion internal to the structure occurs on the rear porch where there is sufficient oxygen. Despite the lack of oxygen in the attic, the wood would continue to pyrolyze due to the high heat fluxes, therefore continue to produce additional gas phase fuel \cite{SFPE:Heskestad}. In the attic, combustion occurred at the external vents as a lack of oxygen present prevented combustion.  After additional wall breaches occur at 45~s and 55~s (see Table~\ref{tab:vents}), the abrupt change in ventilation causes the HRR to increase to 9~MW before it decreases to approximately 6~MW. The HRR then increases towards a sustainable steady-state value.

>>>>

In Fig.~\ref{fig:hrr}, the solid line represents the baseline FDS simulation (this follows the noted door openings from the incident). The dashed line represents an alternative series of events in which the rear door does not get opened and the subsequent breach of the rear porch wall on the left side of the structure does not occur. The dash-dotted line represents the prescribed (or nominal) HRR that was input into FDS. As shown in Fig.~\ref{fig:hrr}, the HRR output from FDS is less than the prescribed HRR because the fire in the structure becomes ventilation limited. The maximum HRR value is slightly less than 9~MW before the fire becomes ventilation limited and begins to decay. The HRR is reduced to 5~MW as the oxygen inside the structure is consumed. There is an insufficient amount of oxygen in the structure to burn all of the fuel, therefore combustion occurs locally at the vents where fresh air is available. Figure~\ref{fig:smv_ext_fire} shows flaming combustion through the failed window on the rear side of the structure and attic breach just after the second fire ignites at 40~s. Figure~\ref{fig:smv_ext_fire} also shows a photograph taken during an attic fire experiment that confirms this type of fire behavior. \textcolor{red}{As the fire becomes underventilated, the majority of the combustion internal to the structure occurs on the rear porch where there is sufficient oxygen. Despite the lack of oxygen in the attic, solid fuel would to pyrolyze due to the high internal temperatures and heat fluxes and therefore continue to produce additional gas phase fuel \cite{SFPE:Heskestad}. In the attic, combustion occurs at the external vents as a lack of oxygen present prevents combustion internal to the structure.} After additional wall breaches occur at 45~s and 55~s (see Table~\ref{tab:vents}), the abrupt change in ventilation causes the HRR to increase to 9~MW before it decreases to approximately 6~MW. The HRR then increases towards a sustainable steady-state value.
